\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-15 trunk/arch.tex
updates

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t0}
  \caption{\small Shopping example: A plan produced before
    synchronization.  Tokens in red indicate observations, tokens in
    blue the goal that this plan attempts to solve for. Arrows
    indicate temporal constraints.}
  \label{fig:shop:exec0}
\end{figure}

Consider that at the next tick $\tau' = \tau+1$ the reactor managing
agent location is able to change the location state variable to
\texttt{Going}. \rx informs our reactor of this new observation which
is added in the plan structure as a fact -- starting exactly at
$\tau'$ and lasting for an unknown duration which is at least 1
tick. As this new observation is integrated in the plan through
synchronization, the solver can identify the similarity between this
new observation and the next token in the existing plan. This implies
that instead of initiating an exhaustive search of all possible
implications, the synchronization process starts its execution with
the assumption that these new observations are consitent with the
currently maintained plan. As a consequence, at the end of
synchronization we will likely have the plan depicted in
Fig. \ref{fig:shop:exec1}. Which just propagated the information
provided by the new observation in the exisiting plan (restricting in
turn the start time of \texttt{Going} and by propagation of the
constraints \texttt{Go} to be {\em exactly} $\tau'$). While focusing
uniquely on the execution frontier ($\tau'$ in
Fig. \ref{fig:shop:exec1}), the \eu solver took benefit of the
exisiting plan to evaluate a solution that asumes that the observation
is consistent with what was decided inside this reactor.

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t1}
  \caption{Shopping example : Result of synchronization after the {\em
      Going} observation was received by the reactor with the plan
    showed in Fig. \ref{fig:shop:exec0}.}
  \label{fig:shop:exec1}
\end{figure}

This choice is directed not only by some natural heurisitc choices
made in the solver but even more enforced in general by the heuristic
order of the decision point reolution choices for our {\em internla}
state flaw presented in section \ref{sec:arch:sync} {\em\color{red}
  TODO: need to rework the presentation of thee choices so I can refer
  to them more directly -- algorithm or pseudo theorem should do the
  trick}. Should such a flaw be revealed during synchronization --
meaning that the current state of an {\em internal} state varaibale is
not fully grounded -- the sequencing of the choices will atempt first
a conservative choice in term of maintaining previous state, then an
optimisitic choice in term of the execution/advance in our current
plan to finally attempt other choices that were not predicted by the
model. The two first possible choices are strongly directed by the
exisiting plan which help direct the search within this frame. This
often allow to have a synchronization that is much more directed and, 
in nominal cases such as the one we showed resolve the deliberation 
in few steps (often without any backtrack in the search).

The synchronization process is also in this process supporting fully
the tracking of the plan execution as it specifies tokens parameters
such as the time points and allow this to propagate through the plan
in order to idenitfy if the plan remains valid -- as in our example --
or that it cannot be executed as it is. The later is often identified
by the synchronization failing to find a consistent solution. for
example dshould the \texttt{Going} observation we receive be to the
\texttt{hardwareStore}, this would break the current plan of our
reactor as we cannot go simultaneously at 2 different places as
illustrated in Fig. \ref{fig:shop:relax}-1. as synchronization is not
possible in this context our strategy is to fully relax all decisions
made by the previous plan steps by just keeping n the plan all the
past observations in both {\em external} and {\em internal} state
variables and the exsiting {\em internal} goals received by this
reactor (\texttt{Own(Milk)} in our example) resulting on the plrtial
plan sghowned in Fig. \ref{fig:shop:relax}-2. In this process the
reactor inform the agent that all {\em external} goals it requested
for the future are note valid anymore which often result in the ownere
of htese timelines to not have to maintain this goal anynmore.

>>>>

\begin{figure}[!htb]
  \centering
  \subfloat[\small A plan produced before synchronization.]{\label{fig:shop:exec0}\includegraphics[width=0.45\columnwidth]{figs/shoping_exec_t0}}
  \subfloat[\small Result of synchronization after the {\em Going}
  observation was received by the reactor with the plan showed in
    \ref{fig:shop:exec0}.]{\label{fig:shop:exec1}\includegraphics[width=0.48\columnwidth]{figs/shoping_exec_t1}}
    \caption{\small Shopping example: Tokens in red indicate
      observations, tokens in blue the goal that this plan attempts to
      solve for. Arrows indicate temporal constraints. }
  \label{fig:shop:exec}
\end{figure}

Consider that at the next tick $\tau' = \tau+1$ the reactor managing
agent location is able to change the location state variable to
\texttt{Going}. \rx informs our reactor of this new observation which
is added in the plan structure as a fact -- starting exactly at
$\tau'$ and lasting for an unknown duration which is at least 1
tick. As this new observation is integrated in the plan through
synchronization, the solver can identify the similarity between this
observation and the next token in the existing plan. Instead of
initiating an exhaustive search of all possible implications, the
synchronization process starts its execution with the assumption that
these new observations are consistent with the currently maintained
plan. As a consequence, at the end of synchronization the plan
depicted in Fig. \ref{fig:shop:exec1} is likely. This is a result of
propagation of information provided by the new observation in the
existing plan while restricting the start time of \texttt{Going} and
propagating temporal constraints, making \texttt{Go} to start {\em
  exactly} at $\tau'$. In doing so, the \eu solver's focus on the
execution frontier ($\tau'$ in Fig. \ref{fig:shop:exec1}) takes
advantage of the existing plan to evaluate a solution that assumes
that the observation is consistent with what was decided by the
reactor.

% \begin{figure}[!htb]
%   \centering
%   \includegraphics[width=0.7\columnwidth]{figs/shoping_exec_t1}
%   \caption{Shopping example : Result of synchronization after the {\em
%       Going} observation was received by the reactor with the plan
%     showed in Fig. \ref{fig:shop:exec0}.}
%   \label{fig:shop:exec1}
% \end{figure}

This choice is directed not only by heuristic choices made in the
solver but also enforced by the heuristic order of the decision point
resolution choices for the {\em internal} state flaw presented in
Section \ref{sec:arch:sync} \fcomment{TODO: need to rework the
  presentation of thee choices so I can refer to them more directly --
  algorithm or pseudo theorem should do the trick}. Should such a flaw
be revealed during synchronization -- such that the current state of
an {\em internal} state variable is not fully grounded -- the
sequencing of the choices will attempt first a conservative choice in
maintaining previous state and only then try a more optimistic
approach in terms of the \comment{I don't follow this last bit. Is
  this token addition that you're talking about?} execution/advance in
our current plan to finally attempt other choices that were not
predicted by the model. The two first possible choices are strongly
directed by the existing plan which helps direct the search within
this frame. This often allow to have a synchronization that is much
more directed and, in nominal cases such as the one we showed resolve
the deliberation in few steps (often without any backtrack in the
search) \comment{All this is confusing; probably reword}.

The synchronization process also supports the tracking of plan
execution. It does so by specifying token parameters such as time
points that are propagated through the plan in order to identify if
the plan remains valid -- as in our example -- or that it cannot be
executed as it is. The later is often identified by the
synchronization failing to find a consistent solution. for example
dshould the \texttt{Going} observation we receive be to the
\texttt{hardwareStore}, this would break the current plan of our
reactor as we cannot go simultaneously at 2 different places as
illustrated in Fig. \ref{fig:shop:relax}-1. as synchronization is not
possible in this context our strategy is to fully relax all decisions
made by the previous plan steps by just keeping n the plan all the
past observations in both {\em external} and {\em internal} state
variables and the exsiting {\em internal} goals received by this
reactor (\texttt{Own(Milk)} in our example) resulting on the plrtial
plan sghowned in Fig. \ref{fig:shop:relax}-2. In this process the
reactor inform the agent that all {\em external} goals it requested
for the future are note valid anymore which often result in the ownere
of htese timelines to not have to maintain this goal anynmore.
